Predicting _C. difficile_ Infection Severity from the Taxonomic Composition of the Gut Microbiome

### 2023-05-16 paper/paper.qmd
Tweak software citations

### Balanced precision

@@

The complete workflow, code, and supporting files required to reproduce this
manuscript with accompanying figures is available at
https://github.com/SchlossLab/severe-CDI.
<!-- TODO update GitHub URL once accepted to journal -->

The steps for machine learning, making figures, and rendering the manuscript
were defined with Snakemake [@koster_snakemake_2012] using a custom version of the
mikropml Snakemake workflow [@sovacool_mikropml_2023].
Dependencies were managed with conda environments.
In addition to the software already cited above, other packages used in the
creation of this manuscript include
schtools [@sovacool_schtools_2022],
Quarto,
ggtext [@wilke_ggtext_2020],
ggsankey [@sjoberg_ggsankey_2022],
cowplot [@wilke_cowplot_2020], and
vegan [@oksanen_vegan_2022].

>>>>

Balanced precision

@@

The complete workflow, code, and supporting files required to reproduce this
manuscript with accompanying figures is available at
<https://github.com/SchlossLab/severe-CDI>.
<!-- TODO update GitHub URL once accepted to journal -->

The workflow was defined with Snakemake [@koster_snakemake_2012] using a custom
version of the mikropml Snakemake workflow [@sovacool_mikropml_2023].
Dependencies were managed with conda environments.
Scripts were written in R [@r_core_team_r_2020],
Python [@van_rossum_python_2009],
and GNU bash.
In addition to the software already cited above, other packages used in the
creation of this manuscript include
cowplot [@wilke_cowplot_2020],
ggtext [@wilke_ggtext_2020],
ggsankey [@sjoberg_ggsankey_2022],
schtools [@sovacool_schtools_2022],
the tidyverse metapackage [@wickham_welcome_2019],
Quarto, and
vegan [@oksanen_vegan_2023].
